---
title: "`r params$title`"
subtitle: "TidyTuesday Data Report"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: bootstrap
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
params:
  dataset_title: "Dataset"
  title: "TidyTuesday Report"
  data_list: NULL
  plots: NULL
  plot_type: "type"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 300
)

# Load required packages
library(ggplot2)
library(gt)
library(dplyr)
```

## Executive Summary

This report provides an overview of the **`r params$dataset_title`** dataset from TidyTuesday. The analysis includes data exploration visualizations and a preview of the dataset structure.

**Report Generated:** `r Sys.time()`

```{r data-info}
# Get basic info about the data
if (!is.null(params$data_list) && length(params$data_list) > 0) {
  first_df <- params$data_list[[1]]
  dataset_names <- names(params$data_list)
  
  cat("**Number of datasets:**", length(params$data_list), "\n")
  cat("**Dataset names:**", paste(dataset_names, collapse = ", "), "\n")
  cat("**Main dataset dimensions:**", nrow(first_df), "rows ×", ncol(first_df), "columns\n")
}
```

## Data Visualization

The following visualization shows the **`r switch(params$plot_type, "type" = "variable types", "na" = "missing data patterns", "cor" = "correlation matrix", "num" = "numeric variable distributions", "cat" = "categorical variable frequencies")`** for the selected dataset(s).

```{r plots, fig.cap=paste("Data visualization:", params$plot_type)}
if (!is.null(params$plots)) {
  if (inherits(params$plots, "gg")) {
    # Single plot
    print(params$plots)
  } else if (is.list(params$plots)) {
    # Multiple plots
    for (i in seq_along(params$plots)) {
      if (inherits(params$plots[[i]], "gg")) {
        print(params$plots[[i]])
      }
    }
  }
} else {
  cat("No visualization available for the current selection.")
}
```

## Data Preview

### Dataset Overview

```{r data-summary}
if (!is.null(params$data_list) && length(params$data_list) > 0) {
  
  for (i in seq_along(params$data_list)) {
    dataset_name <- names(params$data_list)[i]
    df <- params$data_list[[i]]
    
    cat("### Dataset:", dataset_name, "\n\n")
    
    # Create summary table using gt
    summary_data <- data.frame(
      Metric = c("Rows", "Columns", "Missing Values", "Complete Rows", "Data Types"),
      Value = c(
        nrow(df),
        ncol(df),
        sum(is.na(df)),
        sum(complete.cases(df)),
        paste(unique(sapply(df, class)), collapse = ", ")
      ),
      stringsAsFactors = FALSE
    )
    
    summary_table <- summary_data |>
      gt() |>
      gt::tab_header(
        title = paste("Summary Statistics:", dataset_name)
      ) |>
      gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_column_labels()
      ) |>
      gt::tab_style(
        style = gt::cell_fill(color = "#f8f9fa"),
        locations = gt::cells_column_labels()
      )
    
    print(summary_table)
    cat("\n\n")
  }
}
```

### Data Sample

```{r data-preview}
if (!is.null(params$data_list) && length(params$data_list) > 0) {
  
  for (i in seq_along(params$data_list)) {
    dataset_name <- names(params$data_list)[i]
    df <- params$data_list[[i]]
    
    cat("### Sample Data:", dataset_name, "\n\n")
    
    # Show first 10 rows with gt
    preview_df <- head(df, 10)
    
    # Handle wide tables by limiting columns if necessary
    if (ncol(preview_df) > 10) {
      preview_df <- preview_df[, 1:10]
      cat("*Note: Showing first 10 columns only*\n\n")
    }
    
    preview_table <- preview_df |>
      gt() |>
      gt::tab_header(
        title = paste("Data Preview:", dataset_name),
        subtitle = paste("Showing first", min(10, nrow(df)), "rows")
      ) |>
      gt::tab_style(
        style = gt::cell_text(size = "small"),
        locations = gt::cells_body()
      ) |>
      gt::tab_style(
        style = gt::cell_fill(color = "#f8f9fa"),
        locations = gt::cells_column_labels()
      ) |>
      gt::tab_options(
        table.font.size = "small",
        data_row.padding = "3px"
      )
    
    print(preview_table)
    cat("\n\n")
  }
}
```

### Variable Information

```{r variable-info}
if (!is.null(params$data_list) && length(params$data_list) > 0) {
  first_df <- params$data_list[[1]]
  
  # Create variable information table
  var_info <- data.frame(
    Variable = names(first_df),
    Type = sapply(first_df, function(x) class(x)[1]),
    Missing = sapply(first_df, function(x) sum(is.na(x))),
    Missing_Percent = round(sapply(first_df, function(x) sum(is.na(x))/length(x) * 100), 2),
    Unique_Values = sapply(first_df, function(x) length(unique(x))),
    stringsAsFactors = FALSE
  )
  
  var_table <- var_info |>
    gt() |>
    gt::tab_header(
      title = "Variable Information",
      subtitle = names(params$data_list)[1]
    ) |>
    gt::cols_label(
      Variable = "Variable Name",
      Type = "Data Type",
      Missing = "Missing Count",
      Missing_Percent = "Missing %",
      Unique_Values = "Unique Values"
    ) |>
    gt::fmt_number(
      columns = Missing_Percent,
      decimals = 1
    ) |>
    gt::tab_style(
      style = gt::cell_fill(color = "#fff3cd"),
      locations = gt::cells_body(
        columns = Missing_Percent,
        rows = Missing_Percent > 10
      )
    ) |>
    gt::tab_style(
      style = gt::cell_fill(color = "#f8d7da"),
      locations = gt::cells_body(
        columns = Missing_Percent,
        rows = Missing_Percent > 50
      )
    )
  
  print(var_table)
}
```

## Technical Details

**R Version:** `r R.version.string`  
**Report Generated:** `r Sys.time()`  
**TidyTuesday Dataset:** `r params$dataset_title`  

---

*This report was generated automatically using the shrapports package.*
